Topological Equivariant Artist Model

### 2022-03-07 slides/main.tex
testing equivariance

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rrr, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
        \& \& \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
        \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
        \opensetc 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[ru, dashed, maps to, color=sheaf] \& 
        \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
        \& 
        \opensetc^{\prime} 
        \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
        \arrow[ld, dashed, maps to, color=sheaf] 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc^{\prime} 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
        \arrow[rd, dashed, maps to, color=sheaf] 
        \arrow[ru, dashed, maps to, color=sheaf] \& \\
        \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
        \arrow[rrr, "\vartistc^{\prime}", Rightarrow, color=artist]  
        \& \& \& 
        \cgamma{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
        \end{tikzcd}
    \end{equation*}
        $(\vartistc, \vartistc^{\prime})$ are equivariant with respect to $\dfuncc_{\dtotalc}$ if a compatible transform  $\dfuncc_{\dtotalc}$ can be defined such that 
        \begin{equation*}
            \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
        \end{equation*}
        for all points$
        \gbasepointc^{\prime}\in \gbasec^{\prime$
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[rrd, "\delta"'] 
            \arrow[rr, "render"] \&  \& visualization 
            \arrow[d, "measure" description] \\ 
            \&  \&  \&  \& M
            \end{tikzcd}
    \end{equation*}
    \begin{alertblock}{Visual Measurement $\delta$}
        \begin{equation}
            \delta: \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \rightarrow M
        \end{equation}
        $M$ is a measurable component of the rendered visual element, e.g. color, position, shape, texture
    \end{alertblock}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Checking if \vartistc\ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc"', Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] 
            \arrow[rrr, "\equivc", bend left, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[r, "\delta"']\& M 
            \arrow[d, "\dfuncc_{M}", color=action] \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \arrow[rrr, "\equivc"', bend right, color=monoid, dashed] \&  \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc\gtotalc\restriction_{\opensetgc^{\prime}}} 
            \arrow[r, "\delta"] \& M^{\prime}                        
        \end{tikzcd}
    \end{equation*}
        there exists a functor $\equivc: \dfuncc_{\dtotalc} \rightarrow \dfuncc_{M}$ such that 
        \begin{description}
            \item[equivariance] $\equivc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{M}(\equivc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\equivc(\dsectionc(x))) = \equivc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ 
        \end{description} 
\end{frame}

@@

\subsection{Combining Components into Visualizations}

\begin{frame}<presentation:1|handout:0>{Assembly Function $\vmarkc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
            \arrow[rrrr, "\vmarkc", Rightarrow, color=artist] 
            \arrow[ddd, "\dfuncc_{\vtotalc}"', color=action] 
            \& \& \& \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[ddd, "\dfuncc_{\gtotalc}", color=action]  \\
            \& 
            \opensetc 
            \arrow[lu, maps to, color=sheaf] 
             \&  \& 
            \opensetgc 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[ru, maps to, color=sheaf]  \& \\
            \& 
            \opensetc^{\prime} 
            \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
            \arrow[ld, maps to, color=sheaf] 
            \&  \& 
            \opensetgc^{\prime} 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[u, "\dfunchc_{\gtotalc}"', color=action] 
            \arrow[rd, maps to, color=functor] \& \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\vtotalc}\vtotalc\restriction_{\opensetc^{\prime}}}
            \arrow[rrrr, "\vmarkc", Rightarrow, color=artist] 
            \& \&  \& \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}}
            \end{tikzcd}
        \end{equation*}
    \begin{alertblock}{equivariance}
       \begin{equation*}
        \vmarkc(\dfuncc_{\vtotalc}(\vsectionc(\dfunchc_{\vtotalc}^{-1}(\dbasepointc^{\prime})))) = \dfuncc_{\gtotalc}(\vmarkc((\vsectionc(\dfunchc_{\gtotalc}^{-1}(\vindexprec(\dbasepointc^{\prime}))))))
       \end{equation*}
    \end{alertblock}
\end{frame}

>>>>

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rrr, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
        \& \& \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
        \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
        \opensetc 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[ru, dashed, maps to, color=sheaf] \& 
        \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
        \& 
        \opensetc^{\prime} 
        \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
        \arrow[ld, dashed, maps to, color=sheaf] 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc^{\prime} 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
        \arrow[rd, dashed, maps to, color=sheaf] 
        \arrow[ru, dashed, maps to, color=sheaf] \& \\
        \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
        \arrow[rrr, "\vartistc^{\prime}", Rightarrow, color=artist]  
        \& \& \& 
        \cgamma{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
        \end{tikzcd}
    \end{equation*}
        $(\vartistc, \vartistc^{\prime})$ are equivariant with respect to $\dfuncc_{\dtotalc}$ if a compatible transform  $\dfuncc_{\dtotalc}$ can be defined such that 
        \begin{equation*}
            \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
        \end{equation*}
        for all points $\gbasepointc^{\prime}\in \gbasec^{\prime}$
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{Testing if \vartistc\ is equivariant}
    $M$ is a (scaler, vector) measurable component (e.g. color, position, shape, texture, rotation, ) of the rendered visual element.
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[rr, "\vartistc", Rightarrow, color=artist] 
    \arrow[dd, "\equivc"', color=monoid] \&  \& 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[rr, "render"] 
    \arrow[dd, "\extractm", color=monoid] 
    \&  \& 
    visualization 
    \arrow[lldd, "\measure"] \\
    \& \& \& \&  \\
    {Hom(\opensetc, \measure )} 
    \&  \& 
    {Hom(\opensetgc,\measure )} 
    \arrow[ll, "\vindexpushc"', color=functor] 
    \& \& 
    \end{tikzcd}
    \end{equation*}
    \begin{description}
        \item[input]{$\equivc: \dsectionc \mapsto (\opensetc \xrightarrow{\equivc_{\dsectionc}} \measurec)$}
        \item[output]{$\extractmc:\gsectionc \mapsto (\opensetgc \xrightarrow{\extractmc_{\gsectionc}} \measurec)$}
        \item[] $\equivc_{\dsectionc}(\dbasepointc) = \extractmc_{\gsectionc}(\gbasepointc)$ for all $\vindexc(\gbasepointc) = \dbasepointc, \dbasepointc \in \dbasec, \gbasepointc \in \gbasec$ 
    \end{description}
\end{frame}

\begin{frame}<presentation:0|handout:1->{Visual Measurement}
    \begin{columns}
    \column{.5\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \measurec 
            \arrow[rr, "\dfuncc_{\measurec}", color=action] 
            \& \& 
            \measurec^{\prime}\\
            \& \& \\
            \opensetgc 
            \arrow[uu, "\extractmc_{\gsectionc}"] 
            \& \& 
            \opensetgc^{\prime} 
            \arrow[ll, "\dfunchc_{\gtotalc}", color=action] 
            \arrow[uu, "\extractmc_{\dfunctc_{\gtotalc}\gsectionc}"'] 
            \arrow[lluu, "\extractmc_{\dfuncpullc\gsectionc}" description]
        \end{tikzcd}
    \end{equation*}
    \column{.5\textwidth}
    \onslide*<presentation:0|handout:2>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \measurec 
            \arrow[rr, "\dfuncc_{\measurec}", color=action] 
            \& \& 
            \measurec^{\prime}\\
            \& \& \\
            \opensetc 
            \arrow[uu, "\equivc_{\dsectionc}"] 
            \& \& 
            \opensetc^{\prime} 
            \arrow[ll, "\dfunchc_{\dtotalc}", color=action] 
            \arrow[uu, "\equivc_{\dfunctc_{\dtotalc}\dsectionc}"'] 
            \arrow[lluu, "\equivc_{\dfuncpullc\dsectionc}" description]
        \end{tikzcd}
    \end{equation*}
    }
    \end{columns}
    \onslide*<presentation:0|handout:1>{
    $\extractmc_{\gsectionc} \in Hom(\opensetgc, \measurec)$ is a mapping from graphic to visual measurement. $\extractmc_{\gsectionc}$ is a map from an openset $\opensetgc \subseteq \gbasec$ to a measurement $\measurec_{\opensetgc}$ that corresponds to the graphic representation at that region $\gsectionc\restriction_{\opensetgc}$ and the corresponding data $\dsectionc\restriction_{\vindexc\restriction_{\opensetgc}}$.}
    \onslide*<presentation:0|handout:2>{
    $\equivc_{\dsectionc} \in Hom(\opensetc, \measurec)$ is a mapping from data to visual measurement. $\equivc_{\dsectionc}:\dsectionc \mapsto$ is a map from an openset $\opensetc \subseteq \dbasec$ to a measurement $\measurec_{\opensetc}$ that corresponds to the data record at that region $\dsectionc\restriction_{\opensetc}$ and the corresponding graphic $\gsectionc\restriction_{\vindexprec\restriction_{\opensetc}}$
    }
\end{frame}

\begin{frame}<presentation:1|handout:1->
    \frametitle<presentation:0|handout:1>{Using output $\gsectionc$ to check if $\vartistc$ is equivariant}
    \frametitle<presentation:0|handout:2>{Using input $\dsectionc$ to check if $\vartistc$ is equivariant}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] 
            \onslide*<presentation:0|handout:2>{\arrow[rrr, "\equivc", bend left, color=monoid, dashed]} \&  \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[d, "\dfuncc_{\gtotalc}"', color=action]
            \onslide*<presentation:0|handout:1>{\arrow[r, "\delta"]}
            \onslide*<presentation:0|handout:2>{\arrow[r,"\delta \circ \vindexprec"]}
            \& 
            \onslide*<presentation:0|handout:1>{Hom(\opensetgc, \measurec)}
            \onslide*<presentation:0|handout:2>{Hom(\opensetc, \measurec)} 
            \arrow[d, "\dfuncc_{\measurec}", color=action] \\
            \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
            \arrow[rr, "\vartistc", Rightarrow, color=artist] 
            \onslide*<presentation:0|handout:2>{\arrow[rrr, "\equivc"', bend right, color=monoid, dashed]} \&  \& 
            \cgamma{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}} 
            \onslide*<presentation:0|handout:1>{\arrow[r, "\delta"]}
            \onslide*<presentation:0|handout:2>{\arrow[r,"\delta \circ \vindexprec"]} \& 
            \onslide*<presentation:0|handout:1>{Hom(\opensetgc^{\prime}, \measurec^{\prime})}
            \onslide*<presentation:1|handout:2>{Hom(\opensetc^{\prime}, \measurec^{\prime})}                        
        \end{tikzcd}
    \end{equation*}
    \onslide*<presentation:0|handout:1>{
        \begin{align*}
            \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) &= \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))\\
            \extractmc(\dfunctc_{\gtotalc}(\gsectionc(\dfunchc_{\gtotalc})))(\gbasepointc^{\prime}) &= \dfuncc_{\measurec}(\extractmc(\gsectionc))(\gbasepointc^{\prime}) = \extractmc_{\dfunctc_{\gtotalc}\gsectionc}(\gbasepointc^{\prime})
        \end{align*}
    }
    \onslide*<presentation:0|handout:2>{
        \begin{description}
            \item[equivariance] $\equivc(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc})))(\dbasepointc^{\prime}) =\dfuncc_{\measurec}(\equivc(\dsectionc))(\dbasepointc^{\prime})= \equivc_{\dfunctc_{\dtotalc}\dsectionc}(\dbasepointc^{\prime})$ for all $\dbasepointc^{\prime} \in \dbasec^{\prime}$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}\equivc_{\dsectionc}(x) = \equivc_{\dsectionc}(\dbasepointc)$ for all $\dbasepointc \in \dbasec$ 
        \end{description} 
    }
\end{frame}

@@

\subsection{Combining Components into Visualizations}
\begin{frame}<presentation:1|handout:0>{Assembly Function $\vmarkc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&]
            \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} 
            \arrow[rrrr, "\vmarkc", Rightarrow, color=artist] 
            \arrow[ddd, "\dfuncc_{\vtotalc}"', color=action] 
            \& \& \& \& 
            \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
            \arrow[ddd, "\dfuncc_{\gtotalc}", color=action]  \\
            \& 
            \opensetc 
            \arrow[lu, maps to, color=sheaf] 
             \&  \& 
            \opensetgc 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[ru, maps to, color=sheaf]  \& \\
            \& 
            \opensetc^{\prime} 
            \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
            \arrow[ld, maps to, color=sheaf] 
            \&  \& 
            \opensetgc^{\prime} 
            \arrow[ll, "\vindexc"', color=functor] 
            \arrow[u, "\dfunchc_{\gtotalc}"', color=action] 
            \arrow[rd, maps to, color=functor] \& \\
            \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\vtotalc}\vtotalc\restriction_{\opensetc^{\prime}}}
            \arrow[rrrr, "\vmarkc", Rightarrow, color=artist] 
            \& \&  \& \& 
            \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}}
            \end{tikzcd}
        \end{equation*}
    \begin{alertblock}{equivariance}
       \begin{equation*}
        \vmarkc(\dfuncc_{\vtotalc}(\vsectionc(\dfunchc_{\vtotalc}^{-1}(\dbasepointc^{\prime})))) = \dfuncc_{\gtotalc}(\vmarkc((\vsectionc(\dfunchc_{\gtotalc}^{-1}(\vindexprec(\dbasepointc^{\prime}))))))
       \end{equation*}
    \end{alertblock}
\end{frame}
